%------------------------------------------------------------------------------
\section{Results}
\label{sec:results}
\textbf{Kernel-level progression.} Table~\ref{tab:versions} summarizes the DP
kernel on the 1428$\times$968 image (Nsight, first seam).
\textbf{\emph{Fused}} is the structural baseline; \textbf{\emph{GridSync}}
regresses (barrier-bound); \textbf{\emph{Prefetch}} removes the dominant
\texttt{long\_scoreboard} stall and gives the \textbf{largest single jump}
(\textbf{1.67$\times$}); \textbf{\emph{BytePtr}} trims store traffic to reach
the latency floor.

\input{tables/tab_versions.tex}

\textbf{Hardware footprint (Table~\ref{tab:hw}).}
\emph{Fused} and \emph{GridStride} store the full $W$-wide cost row in
shared memory ($5W$ bytes), which reaches 37.5\,KB at 8K yet still fits
within the 96\,KB limit.
\emph{Tiled}'s per-block shared memory is fixed at 0.9\,KB regardless of
$W$ (from Eq.~\eqref{eq:shmem}), enabling 60 independent blocks to coexist
with negligible resource pressure.
Register counts decrease from \emph{Fused} (${\approx}$20) to \emph{Tiled}
(${\approx}$16): \emph{Tiled}'s per-strip loop has fewer live variables than
the CPT-unrolled single-block design.

\input{tables/tab_hw.tex}

\textbf{End-to-end throughput.} Table~\ref{tab:fullresults} gives
whole-pipeline ms/seam for CPU (a single core and the best multicore OpenMP
configuration), \emph{Naive} GPU, the prior single-block best (\emph{Templated} at ${\le}4$K;
\emph{GridStride} at 6K--8K), and \emph{Tiled}.
All rows use the same 50-seam best-of-3 protocol.
Key observations:
\textbf{(1)} At ctrl--4K, \emph{Tiled} beats \emph{Templated} by
\textbf{$1.13$--$1.43\times$} while remaining bit-exact.
\textbf{(2)} At 6K/8K, \emph{Tiled} is \textbf{$2.6\times$} and
\textbf{$3.1\times$} faster than the prior best (\emph{GridStride}).
\textbf{(3)} Over the best multicore CPU baseline (NUMA-aware OpenMP, best of
1--32 threads; Appendix~\ref{app:omp}), \emph{Tiled}'s speedup grows
\emph{monotonically} from \textbf{3.6$\times$} (ctrl) to \textbf{6.2$\times$}
(8K)---larger images engage more of the 60\,SMs. Over a single CPU core the
range is \textbf{16$\times$}--\textbf{57$\times$}.
\textbf{(4)} Kim~et~al.~\cite{kim2015} found their \emph{exact} single-GPU DP
reached only $5.9{\times}$ on their earlier-generation hardware and abandoned
it for the approximate NCSC heuristic. Hardware differs, so this is a
\emph{design}-level point, not a normalized comparison: latency hiding makes
the exact DP they discarded scale well, removing the need to approximate.

\input{tables/tab_full_e2e.tex}

\textbf{Scaling in pixels (Fig.~\ref{fig:scaling}).}
\emph{Tiled}+Prefetch grows sublinearly: a 64$\times$ increase in pixels
(ctrl$\to$8K) costs only ${\sim}18\times$ more time
(0.314$\to$5.73\,ms/seam). Its slope is consistently below \emph{Templated}'s
on images where both run.

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
  width=\columnwidth, height=4.6cm,
  xlabel={image size (megapixels)}, ylabel={ms / seam},
  xlabel near ticks, ylabel near ticks,
  xmin=0, xmax=35, ymin=0, ymax=25,
  legend pos=north west, legend style={font=\scriptsize},
  grid=major, grid style={gray!20},
  xtick={0,5,10,15,20,25,30,35},
]
% Naive: ctrl, 1080p, 2K, 4K, 6K, 8K (baseline: H launches, global R/W)
\addplot[mark=diamond*,gray!70!black,thick,dashed]
  coordinates {(0.52,1.37)(2.07,3.10)(3.69,3.77)(8.29,5.92)(21.2,10.3)(33.2,13.9)};
% Fused: 1080p, 2K, 4K, 6K, 8K (single-block, shared-mem ping-pong)
\addplot[mark=square*,blue,thick]
  coordinates {(2.07,1.94)(3.69,3.08)(8.29,6.73)(21.2,12.63)(33.2,21.3)};
% Templated: ctrl, 1080p, 2K, 4K (fails at 6K/8K, register overflow)
\addplot[mark=triangle*,orange,thick]
  coordinates {(0.52,0.355)(2.07,1.08)(3.69,1.57)(8.29,3.10)};
% Tiled+Prefetch: ctrl, 1080p, 2K, 4K, 6K, 8K
\addplot[mark=*,red,thick]
  coordinates {(0.52,0.314)(2.07,0.917)(3.69,1.25)(8.29,2.16)(21.2,4.16)(33.2,5.73)};
\legend{\emph{Naive}, \emph{Fused}, \emph{Templated} (${\le}4$K), \emph{Tiled}+Prefetch}
\end{axis}
\end{tikzpicture}
\caption{ms/seam vs.\ image size (0.52--33.2\,MP). \textbf{\emph{Tiled}+Prefetch}
has the lowest slope at all sizes and reaches \textbf{57$\times$} over CPU at 8K.
\emph{Templated} stops at 4K (register overflow). The gap to \emph{Fused}
widens with image size.}
\label{fig:scaling}
\end{figure}
